Page not found

### 2023-06-21 manuscript/index.qmd
cover page

# Index {.unnumbered .hidden}

\[TODO : a nice illustration for this, maybe some cool animation ?\]

>>>>

::: {.content-visible when-format="html"}
::: {.content-hidden}
# Cover {.unnumbered}
:::

![Smooth neural fields in $p$ dimensions can be mapped to equivalent neural fields in one dimension, and the dynamics are equivalent.](chapters/figures/fig-cover.svg)
:::
